Analysis paper

### 2021-09-18 analysis/analysis.Rmd
retrospective forecasts

# create plots -----------------------------------------------------------------
# regular forecasts
unfiltered_data[model %in% regular_models] %>%
  forecasts_and_scores()

# ensemble variants

>>>>

# create plots -----------------------------------------------------------------
# regular forecasts
unfiltered_data[model %in% c(regular_models)] %>%
  forecasts_and_scores()

df <- unfiltered_data[model %in% c(regular_models, "Renewal-retrospective", "Convolution-retrospective")]

unfiltered_data$model %>% unique()

df$model %>% unique()
# ensemble variants
